Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

The key findings of this study shed light on educators’ preferences for using
messaging applications supported by their institutions. The literature on
technology adoption often highlights the importance of users' perceptions of the
technology's usefulness and ease of use for its successful implementation and
utilization. However, in the context of higher education, institutions also play
a crucial role in integrating these tools into their educational systems. This
can not only improve the uptake of these applications, but also shape the social
and educational experiences of students. To achieve this successful integration,
institutions should ensure that these messaging applications are (in Europe)
GDPR- (General Data Protection Regulation) compliant to protect students’ data
and provide IT support to all stakeholders who use the applications. In summary,
a technology adoption strategy for instant messaging, including chatbots,
implies an institutional adoption strategy first and foremost.

Comparing these results with those obtained from student surveys in
\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
between teachers’ and students' points of view and intentions when using the
messaging applications in higher education. Teachers are more likely to adopt
technologies that are supported by their institutions. This may be driven by a
desire to ensure that their universities can monitor and support their efforts
to assist students during the learning process, although another reason could
simply be their familiarity with the technological services provided by their
institutions. Meanwhile, students use non-institution messaging applications to
create informal discussion groups with their peers. It is worth noting that peer
support and collaboration are inseparable from learning
\cite{timmis2012constant} and its presence correlates positively with higher
retention in higher education \cite{o2014front}. Therefore, both perspectives
are complementary and play different roles in promoting the learning process;
however, there is a certain degree of incompatibility that would hinder the
process of adoption of a single messaging service that fits the need of both
collectives, or would favor the adoption of semi-informal solutions that would
rely on a popular platform (such as WhatsApp or Telegram) enhanced with
institutional agreements with their providers, as well as locally created and
supported chatbots.

>>>>

The key findings of this study shed light on educators’ preferences for using
messaging applications supported by their institutions. The literature on
technology adoption often highlights the importance of users' perceptions of the
technology's usefulness and ease of use for its successful implementation and
utilization. However, in the context of higher education, institutions also play
a crucial role in integrating these tools into their educational systems. This
does not only improve the uptake of these applications, but also shapes the social
and educational experiences of students. To achieve this successful integration,
institutions should ensure that these messaging applications are (in Europe)
GDPR- (General Data Protection Regulation) compliant to protect students’ data
and provide IT support to all stakeholders who use the applications. In summary,
a technology adoption strategy for instant messaging, including chatbots,
implies an institutional adoption strategy first and foremost.

Comparing these results with those obtained from student surveys in
\cite{MoraChatbots2021:anon}, we now have a clear vision of the differences
between teachers' and students' points of view and intentions when using the
messaging applications in higher education. Teachers are more likely to adopt
technologies that are supported by their institutions. This may be driven by a
desire to ensure that their universities can monitor and support their efforts
to assist students during the learning process, although another reason could
simply be their familiarity with the technological services provided by their
institutions. Meanwhile, students use non-institution messaging applications to
create informal discussion groups with their peers. It is worth noting that peer
support and collaboration are inseparable from learning
\cite{timmis2012constant} and its presence correlates positively with higher
retention in higher education \cite{o2014front}. Therefore, both perspectives
are complementary and play different roles in promoting the learning process;
however, there is a certain degree of incompatibility that would hinder the
process of adoption of a single messaging service that fits the need of both
collectives, or would favor the adoption of semi-informal solutions that would
rely on a popular platform (such as WhatsApp or Telegram) enhanced with
institutional agreements with their providers, as well as locally created and
supported chatbots.
